Streaming CityJSON datasets

### 2024-05-02 paper/main.tex
Spell-check

Futhermore, the CityJSON specification does not prescribe the storage of CityJSONSeq, only the structure of a CityJSONSeq stream (see the five constraints above).
In practice, CityJSONSeq can be stored in a variety of ways, eg in a single file, each feature in a separate file, in a database etc., and the optimal storage solution depends on the implementing application.

@@

\begin{table*}
  \centering
  \begin{threeparttable}
  \caption{The datasets used for the benchmark. }%
  \label{tab:datasets}
  \small
  \begin{tabular}
    {@{}lcccccrrrcrrr@{}}\toprule
    &&  \multicolumn{2}{c}{\textbf{dataset}} && \multicolumn{3}{c}{\textbf{size of file}} && \multicolumn{3}{c}{\textbf{vertices}}   \\ 
    \cmidrule{3-4} \cmidrule{6-8} \cmidrule{10-12} 
     && CityObjects &  app.\footnotesize ${}^{\text{(a)}}$ && CityJSON & CityJSONSeq & compr.\footnotesize ${}^{\text{(b)}}$ && total & largest\footnotesize ${}^{\text{(c)}}$ & shared\footnotesize ${}^{\text{(d)}}$ \\
    \midrule
    \textbf{3DBAG}          && \qty{1110} bldgs    &         && \qty{6.7}{\mega\byte} & \qty{5.9}{\mega\byte} & 12\%  &&     \num{82509} &    \num{4112} &  0.1\% \\
    \textbf{3DBV}           && \qty{71634} diff    &         && \qty{378}{\mega\byte} & \qty{317}{\mega\byte} & 16\%  &&   \num{4110319} &  \num{116670} & 21.0\% \\
    \textbf{Helsinki}       && \qty{77231} bldgs   &         && \qty{572}{\mega\byte} & \qty{412}{\mega\byte} & 28\%  &&   \num{3038576} &    \num{2202} &  0.0\% \\
    \textbf{Helsinki\_tex}  && \qty{77231} bldgs   & tex     && \qty{713}{\mega\byte} & \qty{644}{\mega\byte} & 10\%  &&   \num{3038576} &    \num{2202} &  0.0\% \\
    \textbf{Ingolstadt}     && \qty{55} bldgs      &         && \qty{4.8}{\mega\byte} & \qty{3.8}{\mega\byte} & 25\%  &&     \num{87972} &   \num{12800} &  0.0\% \\
    \textbf{Montréal}       && \qty{294} bldgs     & tex     && \qty{5.4}{\mega\byte} & \qty{4.6}{\mega\byte} & 15\%  &&     \num{31585} &    \num{3393} &  2.0\% \\
    \textbf{NYC}            && \qty{23777} bldgs   &         && \qty{105}{\mega\byte} &  \qty{95}{\mega\byte} & 10\%  &&   \num{1035804} &    \num{2608} &  0.8\% \\
    \textbf{Railway}        && \qty{50} diff       & tex+mat && \qty{4.3}{\mega\byte} & \qty{4.0}{\mega\byte} &  8\%  &&     \num{73554} &   \num{14966} &  0.4\% \\
    \textbf{Rotterdam}      && \qty{853} bldgs     & tex     && \qty{2.6}{\mega\byte} & \qty{2.7}{\mega\byte} & -4\%  &&     \num{22246} &     \num{631} & 20.0\% \\
    \textbf{Vienna}         && \qty{307} bldgs     &         && \qty{5.4}{\mega\byte} & \qty{4.8}{\mega\byte} & 11\%  &&     \num{47220} &    \num{2025} &  0.0\% \\
    \textbf{Zürich}         && \qty{52834} bldgs   &         && \qty{279}{\mega\byte} & \qty{247}{\mega\byte} & 11\%  &&   \num{3472989} &    \num{4069} &  2.6\% \\
    \bottomrule
  \end{tabular}
    \begin{tablenotes}[flushleft]
      \footnotesize
      \item ${}^{\text{(a)}}$ appearance: `tex' is textures stored; `mat' is material stored
      \item ${}^{\text{(b)}}$ compression factor is $\frac{size(CityJSON) - size(CityJSONSeq)}{size(CityJSON)}$
      \item ${}^{\text{(c)}}$ number of vertices in the largest feature of the stream
      \item ${}^{\text{(d)}}$ percentage of vertices that are used to represent different city objects (\eg\ the vertices of a wall shared by two buildings)
    \end{tablenotes}
  \end{threeparttable}
\end{table*}

@@

The number of shared vertices between different city objects also influences the compression factor. 
Shared vertices are those used to represent walls incident to two adjacent buildings.
In CityJSON they are conceptually the same vertices and each of the surfaces refer to them, but in CityJSONSeq they have to be listed separately in each of the buildings.
It should be said that most of the datasets have very few vertices that are shared (most have less than 2\%).
To understand the correlation between the compression factor and the percentage of shared vertices in a datasets, we have modified the script to generate random cuboid buildings: the distribution of the buildings is not random, we have enforced that several buildings are adjacent to others (so that they share vertices with other buildings).
The relationship between the compression and the percentage of shared vertices can be seen in Figure~\ref{fig:compression_adjacent} for around 100 datasets containing exactly \num{1000000} buildings.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/compression_adjacent.pdf}
  \caption{Compression factor of CityJSONSeq files with respect to the percentage of shared vertices in a dataset that was synthetically generated.}% 
\label{fig:compression_adjacent}
\end{figure}
If the number of shared vertices is 0\% this means that we have \num{1000000} buildings that are disconnected; in this case we obtain a compression factor of around 8\% (as was the case in Figure~\ref{fig:compression_random}).
If all the buildings are adjacent to another one (thus nearly 100\% of the vertices are shared), then we can see that the compression factor is about -10\% (which means that the size of the CityJSONSeq file is larger than that of the CityJSON file).
%

@@

From a practitioners point-of-view, we should stress that CityJSONSeq can easily be processed with \emph{Unix pipes} (also called \emph{pipelines}).
Pipelines allow us to chain several processes together, the output of a process becomes the input of the next one, and so on. 
Given 2 processes, the 2nd one can usually start before the 1st one has finished processing all the data.
This means that, in practice, the processing of a dataset can be performed by writing several programs that perform a few small/atomic tasks; this makes the development and maintenance of code simpler.
Moreover, it allows us to write the code in different languages. 
The pipelines used for preparing the datasets used in this paper were actually a mix of Python (the program `cjio' and `cjdb') and Rust (`cjseq' and `cjval'), and another program written in C++ could easy be added.

>>>>

Furthermore, the CityJSON specification does not prescribe the storage of CityJSONSeq, only the structure of a CityJSONSeq stream (see the five constraints above).
In practice, CityJSONSeq can be stored in a variety of ways, eg in a single file, each feature in a separate file, in a database etc., and the optimal storage solution depends on the implementing application.

@@

\begin{table*}
  \centering
  \begin{threeparttable}
  \caption{The datasets used for the benchmark. }%
  \label{tab:datasets}
  \small
  \begin{tabular}
    {@{}lcccccrrrcrrr@{}}\toprule
    &&  \multicolumn{2}{c}{\textbf{dataset}} && \multicolumn{3}{c}{\textbf{size of file}} && \multicolumn{3}{c}{\textbf{vertices}}   \\ 
    \cmidrule{3-4} \cmidrule{6-8} \cmidrule{10-12} 
     && CityObjects &  app.\footnotesize ${}^{\text{(a)}}$ && CityJSON & CityJSONSeq & compr.\footnotesize ${}^{\text{(b)}}$ && total & largest\footnotesize ${}^{\text{(c)}}$ & shared\footnotesize ${}^{\text{(d)}}$ \\
    \midrule
    \textbf{3DBAG}          && \qty{1110} bldgs    &         && \qty{6.7}{\mega\byte} & \qty{5.9}{\mega\byte} & 12\%  &&     \num{82509} &    \num{4112} &  0.1\% \\
    \textbf{3DBV}           && \qty{71634} diff    &         && \qty{378}{\mega\byte} & \qty{317}{\mega\byte} & 16\%  &&   \num{4110319} &  \num{116670} & 21.0\% \\
    \textbf{Helsinki}       && \qty{77231} bldgs   &         && \qty{572}{\mega\byte} & \qty{412}{\mega\byte} & 28\%  &&   \num{3038576} &    \num{2202} &  0.0\% \\
    \textbf{Helsinki\_tex}  && \qty{77231} bldgs   & tex     && \qty{713}{\mega\byte} & \qty{644}{\mega\byte} & 10\%  &&   \num{3038576} &    \num{2202} &  0.0\% \\
    \textbf{Ingolstadt}     && \qty{55} bldgs      &         && \qty{4.8}{\mega\byte} & \qty{3.8}{\mega\byte} & 25\%  &&     \num{87972} &   \num{12800} &  0.0\% \\
    \textbf{Montréal}       && \qty{294} bldgs     & tex     && \qty{5.4}{\mega\byte} & \qty{4.6}{\mega\byte} & 15\%  &&     \num{31585} &    \num{3393} &  2.0\% \\
    \textbf{NYC}            && \qty{23777} bldgs   &         && \qty{105}{\mega\byte} &  \qty{95}{\mega\byte} & 10\%  &&   \num{1035804} &    \num{2608} &  0.8\% \\
    \textbf{Railway}        && \qty{50} diff       & tex+mat && \qty{4.3}{\mega\byte} & \qty{4.0}{\mega\byte} &  8\%  &&     \num{73554} &   \num{14966} &  0.4\% \\
    \textbf{Rotterdam}      && \qty{853} bldgs     & tex     && \qty{2.6}{\mega\byte} & \qty{2.7}{\mega\byte} & -4\%  &&     \num{22246} &     \num{631} & 20.0\% \\
    \textbf{Vienna}         && \qty{307} bldgs     &         && \qty{5.4}{\mega\byte} & \qty{4.8}{\mega\byte} & 11\%  &&     \num{47220} &    \num{2025} &  0.0\% \\
    \textbf{Zürich}         && \qty{52834} bldgs   &         && \qty{279}{\mega\byte} & \qty{247}{\mega\byte} & 11\%  &&   \num{3472989} &    \num{4069} &  2.6\% \\
    \bottomrule
  \end{tabular}
    \begin{tablenotes}[flushleft]
      \footnotesize
      \item ${}^{\text{(a)}}$ appearance: `tex' is textures stored; `mat' is material stored
      \item ${}^{\text{(b)}}$ compressi{}on factor is $\frac{size(CityJSON) - size(CityJSONSeq)}{size(CityJSON)}$
      \item ${}^{\text{(c)}}$ number of vertices in the largest feature of the stream
      \item ${}^{\text{(d)}}$ percentage of vertices that are used to represent different city objects
    \end{tablenotes}
  \end{threeparttable}
\end{table*}

@@

The number of shared vertices between different city objects also influences the compression factor. 
Shared vertices are those used to represent walls incident to two adjacent buildings.
In CityJSON they are conceptually the same vertices and each of the surfaces refer to them, but in CityJSONSeq they have to be listed separately in each of the buildings.
It should be said that most of the datasets have very few vertices that are shared (most have less than 2\%, except 2 datasets have around 20\%).
To understand the correlation between the compression factor and the percentage of shared vertices in a datasets, we have modified the script to generate random cuboid buildings: the distribution of the buildings is not random, we have enforced that several buildings are adjacent to others (so that they share vertices with other buildings).
The relationship between the compression and the percentage of shared vertices can be seen in Figure~\ref{fig:compression_adjacent} for around 100 datasets containing exactly \num{1000000} buildings.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/compression_adjacent.pdf}
  \caption{Compression factor of CityJSONSeq files with respect to the percentage of shared vertices in a dataset that was synthetically generated.}% 
\label{fig:compression_adjacent}
\end{figure}
If the number of shared vertices is 0\% this means that we have \num{1000000} buildings that are disconnected; in this case we obtain a compression factor of around 8\% (as was the case in Figure~\ref{fig:compression_random}).
If all the buildings are adjacent to another one (thus nearly 100\% of the vertices are shared), then we can see that the compression factor is about -10\% (which means that the size of the CityJSONSeq file is larger than that of the CityJSON file).
%

@@

From a practitioners point-of-view, we should stress that CityJSONSeq can easily be processed with \emph{Unix pipes} (also called \emph{pipelines}).
Pipelines allow us to chain several processes together, the output of a process becomes the input of the next one, and so on. 
Given 2 processes, the 2nd one can usually start before the 1st one has finished processing all the data.
This means that, in practice, the processing of a dataset can be performed by writing several programs that perform a few small/atomic tasks; this makes the development and maintenance of code simpler.
Moreover, it allows us to write the code in different languages. 
The pipelines used for preparing the datasets used in this paper were actually a mix of Python (the program \emph{cjio} and \emph{cjdb}) and Rust (\emph{cjseq} and \emph{cjval}), and another program written in C++ could easy be added.
